---
title: "Q1 QBR Data QC"
format: html 
execute:
  echo: false
  warnings: false
prefer-html: true
---

```{r}
# NOTE: change to `format: docx` when rendering to share w/ team

#| output: false
# some silencing code
options(dplyr.summarise.inform = FALSE)
options(tidyverse.quiet = TRUE)

# setup and data wrangling
library(tidyverse)
library(flextable)

# Original data wrangling, with Metro data
#q1_2024 <- readxl::read_xlsx('q1_2024_qbr.xlsx',sheet='q1_2024_qbr') %>%
#  full_join(readxl::read_xlsx('q1_2024_qbr.xlsx',sheet='campaign_key')) %>%
  # remove all campaigns w/ all 0 data
#  mutate(all_data = Sent + Delivered + Opens + `Total Clicks`) %>% filter(all_data != 0) %>% select(-all_data) 

# Data wrangling w/ fake data for demo purposes
q1_2024 <- read_csv('fake_qbr.csv')
```

#### Notes/FYI

-   Pulled all Q1 and 2024 campaigns (using Quarter and Year cols) from Data Repository (pulled in some older campaigns w/ 0 data, see notes later to confirm if we are including in QBR)
-   Using 'CampaignKey' tab (from Ben's xlsx) as source of truth for all clean campaign names, cadence, channel, categories. (Not using corresponding cols that were based on formula lookups in excel; there was lots of missing data bits)
-   Will we need to break out anything by touch and/or segment? Need QC there?
-   Caro still working on QoQ performance changes
-   Caro still working on benchmarks: Rolling 6 month benchmarks will be using Q4 2023 and Q1 2024 data

## List of all campaigns, by campaign category and clean campaign name

Questions:

-   Do we need to include any of the 'Other' campaigns? They look like service messages that could be excluded?
-   Do these cleaned campaign names look correct? Can we combine touches and/or segments for the charts/tables? (in previous QBRs we have combined)
-   Are these the correct buckets? ACP, Brand/Loyalty, Device, Enterprise, HSI, Onboarding, VAS/Revenue
-   Correct campaigns in each bucket?

Please fill in notes category with the correct category and/or clean campaign name if any of these need to be corrected.

```{r}
q1_2024 %>% 
  select(Category_clean,`Clean Campaign Name`,JMID) %>%
  filter(`Clean Campaign Name` %in% c(
    'Anniversary',
    'T Life Messaging',
    'Samsung A7 Lite',
    'Samsung A15',
    'Pre2Post Ad Hoc',
    'Pre2Post Recurring',
    'HSI GW',
    'HSI GW Promo',
    'HSI Onboarding',
    'HSI Voice Onboarding'
  )) %>%
  distinct() %>%
  group_by(Category_clean,`Clean Campaign Name`,JMID) %>% 
  mutate(Notes = '',JMID = as.character(JMID)) %>%
  arrange(Category_clean,`Clean Campaign Name`) %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

## Performance by campaign category

Questions:

-   Does anything look odd here?
-   Any deployment issues to call out?
-   Missing anything?
-   Do we need to include 'Other' campaigns? (Might all be service messages? See table/list above)

```{r}
q1_2024 %>% 
  group_by(Category_clean) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE)))%>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

## Performance by cadence

Questions:

-   What should blanks be categorized as? Removed because they are service messages? (All campaigns missing Cadence are 'Other' category)
-   Does anything look odd here?
-   Any deployment issues to call out?
-   Missing anything?

```{r}
q1_2024 %>% 
  group_by(Cadence_clean) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE)))%>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

##### Campaigns missing cadence:

Please fill in notes category with the correct cadence if any of these should be included. Or confirm that we are excluding all of these from the QBR.

```{r}
q1_2024 %>% 
  filter(is.na(Cadence_clean)) %>%
  select(Cadence_clean,`Clean Campaign Name`,Category_clean) %>%
  distinct() %>%
  mutate(Notes = '',
         Cadence_clean = 'missing') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

## Performance by channel

Questions:

-   Should 'Other' category campaigns be removed? Service messages?
-   Does anything look odd here?
-   Any deployment issues to call out?
-   Missing anything?

```{r}
q1_2024 %>% 
  mutate(is_other = if_else(Category_clean == 'Other','Other','')) %>%
  group_by(is_other,Channel_clean) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE)))%>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

------------------------------------------------------------------------

## More granular QC

Now we're getting into performance by individual campaigns, grouped by bucket. There are many campaigns that were categorized as Q1 2024 campaigns but don't have any send/delivery/open/click data. Can we safely omit these from the QBR? Please indicate in appropriate Notes section if we *should* include a campaign with 0 data. Else I will remove all campaigns with 0 data.

*Please make a note if anything looks unexpected and/or not right. Or should be excluded from the report.*

------------------------------------------------------------------------

#### Performance by Category: ACP

```{r}
q1_2024 %>% 
  filter(Category_clean == 'ACP') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: Brand/Loyalty

Should 'T Life Messaging' campaign clicks be combined with another campaign? Odd to only have clicks.

```{r}
q1_2024 %>% 
  filter(Category_clean == 'Brand/Loyalty') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: Device

```{r}
q1_2024 %>% 
  filter(Category_clean == 'Device') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: Enterprise

```{r}
q1_2024 %>% 
  filter(Category_clean == 'Enterprise') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: HSI

```{r}
q1_2024 %>% 
  filter(Category_clean == 'HSI') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: Onboarding

```{r}
q1_2024 %>% 
  filter(Category_clean == 'Onboarding') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: VAS/Revenue

```{r}
q1_2024 %>% 
  filter(Category_clean == 'VAS/Revenue') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

#### Performance by Category: Other

These are probably service messages that shouldn't be included in QBR? Please confirm.

```{r}
q1_2024 %>% 
  filter(Category_clean == 'Other') %>%
  group_by(`Clean Campaign Name`) %>%
  summarise(sent=scales::label_comma()(sum(Sent, na.rm = TRUE)),
            delivered=scales::label_comma()(sum(Delivered, na.rm = TRUE)),
            dr = scales::label_percent(accuracy = 0.1)(sum(Delivered,na.rm = TRUE)/sum(Sent, na.rm = TRUE)),
            opens=scales::label_comma()(sum(Opens,na.rm = T)),
            or=scales::label_percent(accuracy=.01)(sum(Opens,na.rm = T)/sum(Delivered,na.rm = T)),
            clicks=scales::label_comma()(sum(`Total Clicks`, na.rm = TRUE)),
            ctr = scales::label_percent(accuracy = 0.01)(sum(`Total Clicks`, na.rm = TRUE)/sum(Delivered, na.rm = TRUE))) %>%
  mutate(Notes = '') %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```

------------------------------------------------------------------------

# Language (English vs Spanish)

-   Are we including language breakout in QBR?
-   May be able to categorize from `Action Code` (see table below). Is this valid? Or categorize with JMID or DLIST?
-   If we are including language, please indicate appropriate language for any campaigns that are missing language, or are incorrect based on `Action Code`
-   Note that some campaigns may be deleted from earlier QC, for having 0 data (e.g. Q4’23 ACP Awareness T1)

```{r}
q1_2024 %>% 
  # remove campaigns w/ no data (may elim things w/ no action code)
  mutate(all_data = Sent + Delivered + Opens + `Total Clicks`) %>% filter(all_data != 0) %>% select(-all_data) %>%
  select(Category_clean,`Clean Campaign Name`,`Action Code`,JMID) %>%
  distinct() %>%
  mutate(language = if_else(!is.na(`Action Code`),str_sub(`Action Code`,-2),'unknown')) %>%
  mutate(language = if_else(language %in% c('Y1','RY','ME'),'unknown',language),
         Notes = '',
         JMID = as.character(JMID)) %>%
  #filter(language == 'unknown') %>%
  arrange(Category_clean,`Clean Campaign Name`) %>%
  flextable::flextable() %>% 
  flextable::fontsize(size = 10, part = "body") %>%
  flextable::autofit() %>%
  flextable::border_inner() %>%
  flextable::border_outer() %>%
  flextable::bold(part = 'header') %>%
  flextable::bg(bg='goldenrod1',part='header')
```
